Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-23 analysis/paper/paper.Rmd
Use greyscale and standardise ROPE figures

```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "rstan",
  "tidyr",
  "tools"
)

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code). However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*&reg;. Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;. Intervals in black have a median value that is greater than that of *Phytopathology*&reg;, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*&reg;.', cache=FALSE, fig.env='figure'}

a_y_labs <- rev(gsub("b_abbreviation", "", parameters(m_f1)$Parameter)[-c(1:2)])
a <- plot(equivalence_test(m_f1)) +
  scale_y_discrete(labels = a_y_labs) +
  scale_fill_grey() +
  ggtitle("Code")

b <- plot(equivalence_test(m_f2)) +
  scale_fill_grey() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  ggtitle("Data")

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared. A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared. Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}

@@

a <- plot(m_g1_eq,
          show_labels = TRUE,
          rope_color = "grey10") +
  ggtitle("Code") +
  xlim(-0.3, 0.6) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  coord_flip()

b <-
  plot(m_g2_eq,
       show_labels = TRUE,
       rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
  ) +
  ggtitle("Data") +
  xlim(-0.3, 0.6) +
  coord_flip()

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the impact factor of the publication increases, the likelyhood of sharing code or data may increase', cache=FALSE, fig.env='figure'}
m_h1_eq <- equivalence_test(m_h1)
m_h2_eq <- equivalence_test(m_h2)

@@

a <- plot(m_h1_eq,
          show_labels = TRUE,
          rope_color = "grey10") +
  ggtitle("Code") +
  xlim(-0.2, 1.1) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  coord_flip()

b <-
  plot(m_h2_eq,
       show_labels = TRUE,
       rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    legend.position = "none"
  ) +
  ggtitle("Data") +
  xlim(-0.2, 1.1) +
  coord_flip()

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
```

>>>>

```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "cowplot",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "rstan",
  "tidyr",
  "tools"
)

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code). However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*&reg;. Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
m_f1_eq <- equivalence_test(m_f1)
m_f2_eq <- equivalence_test(m_f2)

m_f1_eq <-
  filter(m_f1_eq,
         Parameter != "b_Intercept[1]" &
           Parameter != "b_Intercept[2]")

m_f2_eq <-
  filter(
    m_f2_eq,
    Parameter != "b_Intercept[1]" &
      Parameter != "b_Intercept[2]" &
      Parameter != "b_Intercept[3]"
  )

ylabs <- gsub("b_abbreviation", "", m_f1_eq$Parameter)

a <- plot(m_f1_eq,
          show_labels = TRUE,
          rope_color = "grey50") +
  ggtitle("Code") +
  scale_y_discrete(labels = rev(ylabs)) +
  scale_fill_manual(
    values =  "grey70"
  ) +
  theme(legend.position = "none") +
  xlim(-3.5, 3.5) +
  xlab("") +
  ylab("Journal Abbreviation")

b <-
  plot(m_f2_eq,
       show_labels = TRUE,
       rope_color = "grey70") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(values = c("grey100", "grey70")) +
  ggtitle("Data") +
  xlab("") +
  xlim(-3.5, 3.5)

# get legend
legend_b <- get_legend(b)

b <- b + theme(legend.position = "none")

p <- plot_grid(a, b,
               ncol = 2,
               rel_widths = c(1, 0.675),
               labels = c("A", "B"),
               label_x = 0.85,
               label_y = 0.9)
p <-
  add_sub(
    p,
    "95% Highest Density Region of Posterior Samples",
    y = 2,
    x = 0.6,
    vpadding = grid::unit(0, "lines")
  )

p <- plot_grid(p, legend_b, nrow = 2, rel_heights = c(1, 0.1))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared. A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided. Here, year is treated as a continous variable to determine if there are changes over time in the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}

@@

a <- plot(m_g1_eq,
          show_labels = TRUE,
          rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    legend.box.spacing = unit(40, "pt")
  ) +
  xlim(-0.3, 0.7) +
  scale_fill_manual(values = "grey70") +
  ggtitle("Code") +
  coord_cartesian(ylim = c(0.9, 6), expand = FALSE)

b <-
  plot(m_g2_eq,
       show_labels = TRUE,
       rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.box.spacing = unit(40, "pt")
  ) +
  xlim(-0.3, 0.7) +
  scale_fill_manual(values = "black") +
  ggtitle("Data") +
  coord_cartesian(ylim = c(0.8, 20), expand = FALSE)

p <- plot_grid(
  a,
  b,
  ncol = 2,
  rel_widths = c(1, 1),
  labels = c("A", "B"),
  label_x = 0.85,
  label_y = 0.9
)

p <-
  add_sub(
    p,
    "95% Highest Density Region of Posterior Samples",
    y = 6,
    x = 0.6,
    vpadding = grid::unit(0, "lines")
  )

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided. Here, impact factor is a continous variable to determine if greater or lesser impact factor values affect the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
m_h1_eq <- equivalence_test(m_h1)
m_h2_eq <- equivalence_test(m_h2)

@@

a <- plot(m_h1_eq,
          show_labels = TRUE,
          rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none"
  ) +
  xlim(-0.2, 1.1) +
  scale_fill_manual(values = "grey70") +
  ggtitle("Code") +
  coord_cartesian(ylim = c(0.9, 4.5), expand = FALSE)

b <-
  plot(m_g1_eq,
       show_labels = TRUE,
       rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank()
  ) +
  xlim(-0.2, 1.1) +
  scale_fill_manual(values = "grey70") +
  ggtitle("Data") +
  coord_cartesian(ylim = c(0.9, 6), expand = FALSE)

# get legend
legend_b <- get_legend(b)

b <- b + theme(legend.position = "none")

p <- plot_grid(
  a,
  b,
  ncol = 2,
  rel_widths = c(1, 1),
  labels = c("A", "B"),
  label_x = 0.85,
  label_y = 0.9
)

p <-
  add_sub(
    p,
    "95% Highest Density Region of Posterior Samples",
    y = 1,
    x = 0.6,
    vpadding = grid::unit(0, "lines")
  )

p <- plot_grid(p, legend_b, nrow = 2, rel_heights = c(1, 0.1))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
```
